---
title: "Steming & Lematization"
output: html_document
---

In the following section we will learn about Stemming & Lemmatization. Let's start with loading required packages

Lets read a Webpage for this purpose

```{r}
library(textstem)

```
Stemming
```{r}
dw <- c('driver', 'drive', 'drove', 'driven', 'drives', 'driving')

stem_words(dw)

```
Lemmatizing

```{r}

lemmatize_words(dw)

```
The most visible difference of stemming and lemmatizing can be seen while working 
with "Be" verbs
```{r}
bw <- c('are', 'am', 'being', 'been', 'be')
stem_words(bw)
```


```{r}
lemmatize_words(bw)
```


```{r}
library(stringr)
sent <- unlist(tokenizers::tokenize_words(sentences))
head(data.frame(cbind(stem_words(sent),lemmatize_words(sent))),20)
```
We will discuss three process of generating lemma,
The first process uses koRpus package and Treetagger to generate lemma dictionary
Treetagger is a external instllation and in the most relaible among all three methods. It takes time but gives the most accurate reasult
```{r}
lemma_dictionary_tt <- make_lemma_dictionary(sent, engine = 'treetagger')
lemma_dictionary_tt %>% 
  head(20)
```

the second process uses hunspell package to create lemma dictionary
```{r}
lemma_dictionary_hs <- make_lemma_dictionary(sent, engine = 'hunspell')
lemma_dictionary_hs %>% 
  head(20)
```

the third process takes lexicon package to generate lemma dictionary
```{r}
lemma_dictionary_lx <- make_lemma_dictionary(sent, engine = 'lexicon')
lemma_dictionary_lx %>% 
  head(20)
```
We will use the lemma_dictionary_tt in the "sentence" dataset. the function we will use is lemmatize_strings(). This will first tke sentences , create tokens, math with the dictionary, and finally create sentences again with the new words found in the dictionary  

```{r}
data.frame(cbind(lemmatize_strings(sentences, dictionary = lemma_dictionary_tt),sentences)) %>% 
  head(20)
```
Lets try with another dictionary

```{r}
data.frame(cbind(lemmatize_strings(sentences, dictionary = lemma_dictionary_hs),sentences))%>% 
  head(20)
```